Lineal regression with one variable and one parameter for the cost function

### 2016-06-29 LinearRegression/Documentation/OneParam/OneParam.tex
starting gradient decendent explanation

    The objective of this function is to actualize the parameter $\theta$
    of the cost function J minimizing the error in each iteration, this
    is done by searching the path to the global minimum. \\

    \begin{figure}[ht!]
        \begin{tikzpicture}
            \begin{axis}[
                         xlabel=$\theta$,
                         ylabel=$J(\theta)$,
                         ymin=0, ymax=25,
                         xtick=\empty,
                         ytick=\empty
                        ]
                \addplot[mark=none, color=red]{x^2};

@@

    The function that we are going to use is described bellow. The first thing
    to do is replace the function $J(\theta)$

>>>>

    The objective of this function is to actualize the parameter $\theta$
    of the cost function J minimizing the error in each iteration, this
    is done by searching the path to the global minimum.

    for those of you who are not familiar with the derivarives, is highly
    recomendable to look at the Derivative fundamentals article that is in
    located in the documentation directory.\\

    Now lets analyze the formula, the fist simbol is the $\theta$ that is the
    parameter of the cost function, the second is the $:=$ which means assign,
    this make sence because we are trying to update the parameter of the
    function trying to make it as closer to the minimum as possible.

    \begin{figure}[ht!]
        \begin{tikzpicture}
            \begin{axis}[
                         title={Gradient decend with positive derivative},
                         xlabel=$\theta$,
                         ylabel=$J(\theta)$,
                         ymin=0, ymax=25,
                         xtick=\empty,
                         ytick=\empty
                        ]
                \addplot[mark=none, color=red]{x^2};

@@

    \vspace{8cm}

    Now the first thing to do in order to use the gradient desent in our cost
    function is replace the function $J(\theta)$ in the formula
